Leveraging The Progress in Automated Theorem Proving for Program Synthesis\\ \small{WWTF ICT 2022}

### 2022-03-29 WWTF/main.tex
asdf

1) Parigot's $\lambda\mu$-calculus~\cite{Parigot1} gives a direct translation of classical proofs with datatypes and is essentially ready for implementation.
However, since non-intuitionistic tautologies like $\neg\forall xA(x)\to \exists x\neg A(x)$ or $A\vee \neg A$ are assigned a program, we lose the realizability of $\exists$ and $\vee$.
{\color{red} unclear: ``are assigned a program''}
As discussed in~\cite{practical}, in practice it is often possible to eliminate the non-intuitionistic fragments.
{\color{red} unclear: ``fragments''}
We aim to establish stronger theoretical guarantees on when this is possible but also more practical benchmarks on the feasibility of this approach, even when realizability is not ensured by a theorem.
{\color{red} unclear: ``more practical benchmarks''}

2) Sometimes classical validity guarantees intuitionistic validity, most famously for $\Pi_2$-formulas in Arithmetic~\cite{Friedman}. There have been various variations of this result, most notably by Schwichtenberg's group~\cite{schwichtenberg}.
We will adapt their work to our more general setting.
{\color{red} Can the previous sentence be made more concrete? Also why we this promising and feasiable?}
%	
%We expect that in practice these approaches will be sufficient in many situations.

Third, we also investigate a completely new direction:
We aim for a translation between provers rather than proofs. 
E.g., we study under what conditions classic proofs of a modified input formula allow to extract intuitionistic proofs of the actual input.
A promising example is actually the reverse direction:
given an intuitionistic prover one can establish classical provability via double negation translation.
%A first approximation has been outlined in~\cite{RDNT}.

>>>>

1) Parigot's $\lambda\mu$-calculus~\cite{Parigot1} gives a direct translation of classical proofs with datatypes and is essentially ready for implementation.
However, since non-constructive tautologies like $\neg\forall xA(x)\to \exists x\neg A(x)$ or $A\vee \neg A$ {\color{blue} are classically provable}, we lose the realizability of $\exists$ and $\vee$.
As discussed in~\cite{practical}, in practice it is sometimes possible to eliminate the non-constructive reasoning steps from proofs.
We aim to establish stronger theoretical guarantees on when this is possible but also evaluate this approach when realizability is not ensured by a theorem.

2) Sometimes classical validity guarantees intuitionistic validity, most famously for $\Pi_2$-formulas in Arithmetic~\cite{Friedman}. There have been many variations of this result, most notably by Schwichtenberg's group~\cite{schwichtenberg}.
We will collect, adapt and extend these results with regard to our concrete setting. 
This is particularly promising when considering altered specifications (see next point).
%	
%We expect that in practice these approaches will be sufficient in many situations.

Third, we investigate a new direction:
We aim for a translation between provers rather than proofs.
E.g., we study under what conditions classical proofs of a modified input formula allow to extract intuitionistic proofs of the actual input.
A motivating example is actually the reverse direction:
given an intuitionistic prover one can establish classical provability via double negation translation.
%A first approximation has been outlined in~\cite{RDNT}.
